Automatic discovery of circuit structure from neural connectomics

### 2014-01-07 docs/paper.tex
updates to paper; added extra figs

\todo{Do we assign any of the unknown cells correctly?  are types 72-79
“different” or simply unknown?}

@@

The roundworm Caenorhabditis elegans is a model system in
developmental neuroscience\autocite{White1986}, with the location and
connectivity of each of 302 neurons developmentally determined,
leading to early measurement of the connectome. Unlike the retina,
only the motor neurons in c. elegans exhibit regular distribution in
space, being distributed along the body axis. Most interneurons are
concentrated in various ganglia that project throughout the entire
animal, and the sensory neurons are primarily located in a small
number of anterior ganglia.

@@

>>>>

@@

The roundworm Caenorhabditis elegans is a model system in
developmental neuroscience\autocite{White1986}, with the location and
connectivity of each of 302 neurons developmentally determined,
leading to early measurement of the connectome. Unlike the retina,
only the motor neurons in c. elegans exhibit regular distribution in
space -- along the body axis. Most interneurons are
concentrated in various ganglia that project throughout the entire
animal, and the sensory neurons are primarily located in a small
number of anterior ganglia.

@@

\FloatBarrier
\subsection{Detailed learned connectivity for mouse retina}

Here we show the recovered distance-dependent connectivty profile
versus the empirical distance-dependent connectivty for the
retina dataset. The Logistic-distance Poisson likelihood closely
matches the empirical likelihood for most classes.

\begin{figure}[h!]
  \centering 
    \centerline{\includegraphics[width=7in,page=2]{mouseretina/retina.1.2.ld.0.0.data-fixed_20_100-anneal_slow_400.0.latent.pdf}}
  \caption{Learned connectivity vs distance between each of the discovered cell types in the mouse retina. The rows are the source type, and the columns are the destination type. Blue is the empirical plot of the probability of connection vs distance for those two types; red is the learned function}.

\label{fig:supp:mousecompareari}
\end{figure}
